---
title: "Mural_analysis"
author: "Christopher Adams"
date: "10/16/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## FILE PREP
```{r setup_files, echo = FALSE}
library(ggplot2)

# Want to associate mural counts with block groups
setwd("/Users/adamscj/")
census_df <- read.csv("./Desktop/Penn/Jensen_Lab/phillybg.frame.2016.csv")
mural_df <- read.csv("Desktop/Penn/Jensen_Lab/mural_blockgroup_count.csv", sep = '\t', col.names = c('geometry', 'mural_count'), header = TRUE)
block_group_df <- read.csv("Desktop/Penn/Jensen_Lab/formatted_blockgroup_geom.csv", col.names = c("","num_blocks","blockgroup","censustract","area","geometry"), header = FALSE)
combined_mural_block_df = merge(block_group_df, mural_df, by='geometry')
id_col <- paste(combined_mural_block_df$censustract / 100, combined_mural_block_df$blockgroup, sep = "_")
combined_mural_block_df$blockgroupID = id_col
mural_block_df = data.frame('blockgroupID' = combined_mural_block_df$blockgroupID, 'mural_count' = combined_mural_block_df$mural_count)
# join the dataframes
aug_census_df = merge(census_df, mural_block_df, by='blockgroupID')


violent_crime <- rowSums(census_df[27:37])
nonviolent_crime <- rowSums(census_df[38:48])
aug_census_df$violentcrime_total = violent_crime
aug_census_df$nonviolentcrime_total = nonviolent_crime


mural_presence = aug_census_df$mural_count
mural_presence[mural_presence >= 1] <- 1
aug_census_df$mural_presence = as.factor(mural_presence)
with_murals_df = aug_census_df[aug_census_df$mural_count >= 1,]
sans_murals_df = aug_census_df[aug_census_df$mural_count == 0,]
```

## Including Plots

# Make boxplots of variables in mural'ed block groups versus non-mural'ed
```{r boxplots}
library(gridExtra)
library(ggpubr)
#vacantprop boxplot
box_with_df <- data.frame(vacantprop=with_murals_df$vacantprop, comresprop=with_murals_df$comresprop, segregationmetric=with_murals_df$segregationmetric, povertymetric=with_murals_df$povertymetric, violent=with_murals_df$violentcrime_total, nonviolent= with_murals_df$nonviolentcrime_total, mural_presence=rep('Y', nrow(with_murals_df)))
box_wo_df <- data.frame(vacantprop=sans_murals_df$vacantprop, comresprop=sans_murals_df$comresprop, segregationmetric=sans_murals_df$segregationmetric, povertymetric=sans_murals_df$povertymetric,violent=sans_murals_df$violentcrime_total, nonviolent= sans_murals_df$nonviolentcrime_total, mural_presence=rep('N', nrow(sans_murals_df)))
full_box_df <- rbind(box_with_df, box_wo_df)
# Run t-tests
violent_ttest = t.test(box_with_df$violent, box_wo_df$violent)
viol_boxplot <- ggplot(full_box_df, aes(x=mural_presence, y = violent)) +
  geom_boxplot(aes(fill=mural_presence)) +
  stat_compare_means(method = "t.test", comparisons=list(c('Y', 'N')), label.y = 3000) +
  theme(legend.position = 'none', axis.title.x = element_blank(), axis.text.x = element_blank())
nonviolent_ttest = t.test(box_with_df$nonviolent, box_wo_df$nonviolent)
nonviol_boxplot <- ggplot(full_box_df, aes(x=mural_presence, y = nonviolent)) +
  geom_boxplot(aes(fill=mural_presence)) +
  stat_compare_means(method = "t.test", comparisons=list(c('Y', 'N')), label.y = 10000) +
  theme(axis.title.x = element_blank(), axis.text.x = element_blank())
vac_boxplot <- ggplot(full_box_df, aes(x=mural_presence, y = vacantprop)) +
  geom_boxplot(aes(fill=mural_presence)) +
  stat_compare_means(method = "t.test", comparisons=list(c('Y', 'N')), label.y = 0.35) +
  theme(legend.position = 'none', axis.title.x = element_blank(), axis.text.x = element_blank())
com_boxplot <- ggplot(full_box_df, aes(x=mural_presence, y = comresprop)) +
  geom_boxplot(aes(fill=mural_presence)) +
  stat_compare_means(method = "t.test", comparisons=list(c('Y', 'N')), label.y = 0.80) +
  theme(axis.title.x = element_blank(), axis.text.x = element_blank())
seg_boxplot <- ggplot(full_box_df, aes(x=mural_presence, y = segregationmetric)) +
  geom_boxplot(aes(fill=mural_presence)) +
  stat_compare_means(method = "t.test", comparisons=list(c('Y', 'N')), label.y = 0.7) +
  theme(legend.position = 'none')
pov_boxplot <- ggplot(full_box_df, aes(x=mural_presence, y = povertymetric)) +
  geom_boxplot(aes(fill=mural_presence)) +
  stat_compare_means(method = "t.test", comparisons=list(c('Y', 'N')), label.y = 0.8) +
  theme()
grid.arrange(viol_boxplot, nonviol_boxplot, vac_boxplot, com_boxplot, seg_boxplot, pov_boxplot, nrow = 3)
```

# Run t-tests
```{r ttests}
# Run t-tests
violent_ttest = t.test(box_with_df$violent, box_wo_df$violent)

nonviolent_ttest = t.test(box_with_df$nonviolent, box_wo_df$nonviolent)

vacprop_ttest = t.test(box_with_df$vacantprop, box_wo_df$vacantprop)

comresprop_ttest = t.test(box_with_df$comresprop, box_wo_df$comresprop)

segregationmetric_ttest = t.test(box_with_df$segregationmetric, box_wo_df$segregationmetric)

povertymetric_ttest = t.test(box_with_df$povertymetric, box_wo_df$povertymetric)

```

## Logistic Regressions

```{r logistic_setup}
library(caret)
library(plyr)

logreg_df <- data.frame("blockgroupID" = aug_census_df$blockgroupID,
                        "mural_presence" = aug_census_df$mural_presence,
                        "log_income" = log(aug_census_df$income),
                        "pop" = aug_census_df$total,
                        "area" = aug_census_df$area,
                        "black_prop" = aug_census_df$blackprop,
                        "vacantprop" = aug_census_df$vacantprop,
                        "comresprop" = aug_census_df$comresprop,
                        "povertymetric" = aug_census_df$povertymetric)

library(Amelia)
missmap(logreg_df, main = "Missing values vs observed")

```

# Simple logistic regressions
Here I'm going to start running them one by one

```{r run_simple_log_regressions}

# log income model
log_income_model <- glm(data = logreg_df, formula = mural_presence ~ log_income, family = binomial(link = "logit"))

# poverty model
poverty_model <- glm(data = logreg_df, formula = mural_presence ~ povertymetric, family = binomial(link = "logit"))

# pop model
pop_model <- glm(data = logreg_df, formula = mural_presence ~ pop, family = binomial(link = "logit"))

# area model
area_model <- glm(data = logreg_df, formula = mural_presence ~ area, family = binomial(link = "logit"))

# black prop model
black_prop_model <- glm(data = logreg_df, formula = mural_presence ~ black_prop, family = binomial(link = "logit"))

# vacantprop model
vacantprop_model <- glm(data = logreg_df, formula = mural_presence ~ vacantprop, family = binomial(link = "logit"))

# comresprop model
comresprop_model <- glm(data = logreg_df, formula = mural_presence ~ comresprop, family = binomial(link = "logit"))

```

For log income (p = 0.980):
```{r simple_log_income}
summary(log_income_model)
predictions = factor(c(round(predict(log_income_model, logreg_df, type = "response"), digits = 0)))
confusionMatrix(predictions, rev(factor(logreg_df$mural_presence)))
confusionMatrix(predictions, factor(logreg_df$mural_presence))
```

For poverty metric (p = 4.65e-06):
```{r simple_povertymetric}
summary(poverty_model)
predictions = factor(round(predict(poverty_model, logreg_df, type = "response"), digits = 0))
confusionMatrix(predictions, rev(factor(logreg_df$mural_presence)))
confusionMatrix(predictions, factor(logreg_df$mural_presence))
```

For population (p = 0.473):
```{r simple_pop}
summary(pop_model)
predictions = factor(round(predict(pop_model, logreg_df, type = "response"), digits = 0))
confusionMatrix(predictions, factor(logreg_df$mural_presence))
```

For area (p = 0.00869):
```{r simple_area}
summary(area_model)
predictions = factor(round(predict(area_model, logreg_df, type = "response"), digits = 0))
confusionMatrix(predictions, factor(logreg_df$mural_presence))
```

For black proportion (p = 0.857):
```{r simple_blackprop}
summary(black_prop_model)
predictions = factor(round(predict(black_prop_model, logreg_df, type = "response"), digits = 0))
confusionMatrix(predictions, factor(logreg_df$mural_presence))
```

For vacant proportion (p = 6.13e-13):
```{r simple_vacantprop}
summary(vacantprop_model)
predictions = factor(round(predict(vacantprop_model, logreg_df, type = "response"), digits = 0))
confusionMatrix(predictions, factor(logreg_df$mural_presence))
```

For commercial residential proportion (p < 2e-16):
```{r simple_comresprop}
summary(comresprop_model)
predictions = factor(round(predict(comresprop_model, logreg_df, type = "response"), digits = 0))
confusionMatrix(predictions, factor(logreg_df$mural_presence))
```

# Multiple Logistic Regression

```{r multiple_logistic_regression_full}
# with every variable
full_multiple_logreg <- glm(data = logreg_df, formula = mural_presence ~ log_income + povertymetric + pop + area + black_prop + vacantprop + comresprop, family = binomial(link = "logit"))
summary(full_multiple_logreg)
predictions = factor(round(predict(full_multiple_logreg, logreg_df, type = "response"), digits = 0))
confusionMatrix(predictions, factor(logreg_df$mural_presence))
```

```{r multiple logistic_regression_significant_only}
# with only the significant variables from before
sig_multiple_logreg <- glm(data = logreg_df, formula = mural_presence ~ povertymetric + area + vacantprop + comresprop, family = binomial(link = "logit"))
summary(sig_multiple_logreg)
predictions = factor(round(predict(sig_multiple_logreg, logreg_df, type = "response"), digits = 0))
confusionMatrix(predictions, factor(logreg_df$mural_presence))

```

# Decision Trees

```{r simple Decision Tree}
library(rpart)
# with every variable
full_dec_tree <- rpart(data = logreg_df, formula = mural_presence ~ log_income + povertymetric + pop + area + black_prop + vacantprop + comresprop, method = 'class')

pfit_full_dec_tree = prune(full_dec_tree, cp = 
                             full_dec_tree$cptable[which.min(full_dec_tree$cptable[,"xerror"]),"CP"])
plot(pfit_full_dec_tree, uniform = TRUE)
text(pfit_full_dec_tree, use.n=TRUE, all=TRUE, cex=.8)

predictions = predict(pfit_full_dec_tree, logreg_df, type = "class")
confusionMatrix(predictions, factor(logreg_df$mural_presence))
```

```{r random forest}
library(randomForest)
# with every variable
rf_fit <- randomForest(formula = mural_presence ~ log_income + povertymetric + pop + area + black_prop + vacantprop + comresprop, data = logreg_df, ntree=100, importance = TRUE, na.action=na.omit)
imp <- importance(rf_fit, type=1, scale = F)

rf_fit
imp

```

# Model the number of murals when murals exist

```{r number_of_murals_setup}
mural_num_predictors_df <- data.frame("blockgroupID" = aug_census_df$blockgroupID,
                        "mural_count" = aug_census_df$mural_count,
                        "log_income" = log(aug_census_df$income),
                        "pop" = aug_census_df$total,
                        "area" = aug_census_df$area,
                        "black_prop" = aug_census_df$blackprop,
                        "vacantprop" = aug_census_df$vacantprop,
                        "comresprop" = aug_census_df$comresprop,
                        "povertymetric" = aug_census_df$povertymetric)
```

## Simple Linear Regressions

```{r run_simple_log_regressions}

# log income model
log_income_lin_model <- lm(data = mural_num_predictors_df, formula = mural_count ~ log_income)

# poverty model
poverty_lin_model <- lm(data = mural_num_predictors_df, formula = mural_count ~ povertymetric)

# pop model
pop_lin_model <- lm(data = mural_num_predictors_df, formula = mural_count ~ pop)

# area model
area_lin_model <- lm(data = mural_num_predictors_df, formula = mural_count ~ area)

# black prop model
black_prop_lin_model <- lm(data = mural_num_predictors_df, formula = mural_count ~ black_prop)

# vacantprop model
vacantprop_lin_model <- lm(data = mural_num_predictors_df, formula = mural_count ~ vacantprop)

# comresprop model
comresprop_lin_model <- lm(data = mural_num_predictors_df, formula = mural_count ~ comresprop)

```

For log income (p = 0.708), R^2 = 0.00106:
```{r simple_log_income}
summary(log_income_lin_model)
```

For poverty metric (p = 0.000169), R^2 = 0.01061:
```{r simple_povertymetric}
summary(poverty_lin_model)

```

For population (p = 0.24515), y_intercept (p = 0.00182), R^2 = 0.001012:
```{r simple_pop}
summary(pop_lin_model)
```

For area (p = 2.26 e -05), R^2 = 0.01338:
```{r simple_area}
summary(area_lin_model)
```

For black proportion (p = 0.911), yintercept (p=3.46e-11), R^2 = 9e-06:
```{r simple_blackprop}
summary(black_prop_lin_model)
```

For vacant proportion (p = 7.492-09), R^2 = 0.02474:
```{r simple_vacantprop}
summary(vacantprop_lin_model)
```

For commercial residential proportion (p < 2e-16), R^2 = 0.092:
```{r simple_comresprop}
summary(comresprop_lin_model)
```
# Multiple Linear Regression
Running it on all predictors, R^2 = 0.1274
```{r multiple_linear_regression_full}
# with every variable
full_multiple_linreg <- lm(data = mural_num_predictors_df, formula = mural_count ~ log_income + povertymetric + pop + area + black_prop + vacantprop + comresprop)
summary(full_multiple_linreg)
```
Only using the significant predictors from the logistic regression, R^2 = 0.1081
```{r multiple linear_regression_significant_only}
# with only the significant variables from before
sig_multiple_linreg <- lm(data = mural_num_predictors_df, formula = mural_count ~ povertymetric + area + vacantprop + comresprop)
summary(sig_multiple_linreg)
```
# Decision Trees for predicting number of murals

```{r simple Decision Tree for mural count}
library(rpart)
# with every variable
full_dec_tree_mural_count <- rpart(data = mural_num_predictors_df, formula = mural_count ~ log_income + povertymetric + pop + area + black_prop + vacantprop + comresprop, method = 'anova')

pfit = prune(full_dec_tree_mural_count, 
             cp = full_dec_tree_mural_count$cptable[which.min(full_dec_tree_mural_count$cptable[,"xerror"]),"CP"])

plot(pfit, uniform = TRUE)
text(pfit, use.n=TRUE, all=TRUE, cex=.8)

plot(full_dec_tree_mural_count, uniform = TRUE )
text(full_dec_tree_mural_count, use.n=TRUE, all=TRUE, cex=.8)

```